A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-01-22 sections/Overview.tex
overview: other problems with DK's algorithm

\paragraph{Other Challenges} Scoping, Output Contexts?

\subsection{Small-Step Unification} Mention some algorithms for unification for 
dependent types that use a small-step approach. Credit them later for some ideas that 
we also employ.

>>>>

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - 
\paragraph{Complex Scoping and Propagation}

Besides the problematic lemmas in the DK metatheory, there are other reasons to
look for an alternative algorithmic formulation of the type system that is more
amenable to mechanisation. Indeed, two aspects that are particularly
challenging to mechanise are the scoping of universal and existential type
variables, and the propagation of the instantiation of existential type
variables across judgments.

DK is already quite disciplined on these accounts, in particular compared to
traditional constraint-based type-inference algorithms like Algorithm W which
features an implicit global scope for all type variables. Indeed, DK uses an
explicit and ordered context that tracks the relative scope of universal and
existential variables and it is careful to only instantiate existential
variables in a well-scoped manner.

Moreover, DK's algorithm carefully propagates instantiations by recording them
into the context and threading this context through all judgments.  means of
two This means that every judgments takes two contexts---an input and an output
context---rather than the conventional single context. The output context
records any new variable instantations; to propagate these instantiations to
the remaining judgements, their predecessor's output context---which is their
input context---is applied to them as a substitution.

While it works, DK's approach is still fairly involved and thus hard to reason
about in a mechanised setting. Indeed, the instantiations have to be recorded
in the context and are applied incrementally to each remaining judgment in
turn, rather than immediately to all remaining judgments at once. Also the
stack discipline of the ordered contexts does not mesh well with the use of
output contexts; explicit marker entries are needed in two places to
demarcate the end of an existential variable's scope. These are compelling 
reasons to look for a simpler algorithm that is easier to reason about in a 
mechanised setting.

%-------------------------------------------------------------------------------
\subsection{Small-Step Unification} Mention some algorithms for unification for 
dependent types that use a small-step approach. Credit them later for some ideas that 
we also employ.
